Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
abstract

\begin{abstract}
%
Modern control is implemented using digital microcontrollers, which are
designed to work in an embedded environment, within a dynamical plant that
can present physical components.
%
We present a new algorithm based on Counter-Example Guided Inductive
Synthesis that automates the design of digital controllers that are
correct-by-construction.  The synthesis result is sound with respect to the
complete range of approximations, including time discretisation,
quantisation effects, and finite-precision arithmetic and their related
rounding errors.
%
We have implemented our new algorithm in a tool called \tool, and are able
to automatically generate stable controllers for a set of intricate plant
models taken from the literature within minutes.
%
\end{abstract}

>>>>

\begin{abstract}
%
Modern control is implemented using digital microcontrollers, which are
designed to work in an embedded environment, within a dynamical plant that
represents physical components.
%
We present a new algorithm based on counterexample guided inductive
synthesis that automates the design of digital controllers that are
correct by construction.  The synthesis result is sound with respect to the
complete range of approximations, including time discretisation,
quantisation effects, and finite-precision arithmetic and their related
rounding errors.
%
We have implemented our new algorithm in a tool called \tool, and are able
to automatically generate stable controllers for a set of intricate plant
models taken from the literature within minutes.
%
\end{abstract}
